humanCdGF_predict_cfu

### 2016-10-11 code/HumanCdGF_predict_cfu.Rmd
remove boruta

test <- Boruta(log_cfu_med ~ ., data = cfu_shared_colonized.df, maxRuns = 5000)

cfu_shared_colonized <- cfu_shared_colonized.df %>% 
  select(log_cfu_med, one_of(names(test$finalDecision[test$finalDecision %in% c('Confirmed', 'Tentative')])))

set.seed(seed)
rf_all <- randomForest(log_cfu_med ~ ., data = cfu_shared_colonized.df,
                           importance = TRUE, ntree = n_trees, mtry = 14)
set.seed(seed)
rf_bor <- randomForest(log_cfu_med ~ ., data = cfu_shared_colonized,
                           importance = TRUE, ntree = n_trees, mtry = 2)

plot(importance_sorted/max(importance_sorted))
importance_sorted <- sort(importance(rf_bor)[,1], decreasing = T)
top_important_OTU <- rownames(data.frame(importance_sorted[importance_sorted/max(importance_sorted) > 0.6]))

>>>>

set.seed(seed)
rf_all <- randomForest(log_cfu_med ~ ., data = cfu_shared_colonized.df,
                           importance = TRUE, ntree = n_trees, mtry = 14)

importance_sorted <- sort(importance(rf_all)[,1], decreasing = T)
top_important_OTU <- rownames(data.frame(importance_sorted[importance_sorted/max(importance_sorted) > 0.6]))
